Effects of Reynolds Number on the Performance and Near-Wake of a Vertical-Axis Cross-Flow Turbine

### 2015-03-31 paper.tex
Add todo item for XFOIL
Add todo item for Froude number discussion
Add point about CFD model validation and turbulent transition

@@

@@

>>>>

\todo[inline]{Talk about interdependence of Froude number.}

@@

\todo[inline]{Add foil characteristics computed by XFOIL here.}

@@

These results suggest that to validate predictive engineering models, one must
use data of at least this scale, especially high-fidelity CFD models, where
transition to turbulence may be completely different between scaled physical
model and prototype.
